Spatial evolution of solar wind discontinuities in the outer heliosphere

### 2024-11-23 article.qmd
docs: open research

Here, $α$ and $θ$ represent the shape and scale parameters, respectively. The complementary cumulative distribution function of the Weibull distribution $F(τ; α, θ) = 1 - \mathrm{e}^{-(τ/θ)^α}$ is a stretched exponential function.

@@

>>>>

Here, $α$ and $θ$ represent the shape and scale parameters, respectively. The complementary cumulative distribution function of the Weibull distribution $F(τ; α, θ) = 1 - \mathrm{e}^{-(τ/θ)^α}$ is a stretched exponential function (The Weibull distribution reduces to the exponential distribution when $α = 1$).

@@

# Open Research

Codes and datasets used for the analysis are available in the GitHub repository https://github.com/Beforerr/ids_spatial_evolution_juno.
